On the assessment of the ability of measurements, nowcasts, and forecasts to track changes

### 2024-07-29 CoverLetter/letter-to-the-editor.tex
Add medical to summary

%--- set-up for the main part and the closing of the letter:
%\setkomavar{title}{Testtitel} %--- rarely needed, placed before the subject line
\setkomavar{subject}{Submission to BMC Medical Research Methodology} %--- placed before the opening phrase
%\setkomavar{signature}{\includegraphics[width=2.5cm]{unterschrift}\\Jonas Rieger} %--- used by \closing{...}; overwrites the fromname variable
\setkomavar{signature}{[signature to be inserted]\\Jonas Rieger} %--- used by \closing{...}; overwrites the fromname variable
                                             %(you can provide a hand-written signature with \includegraphics)
\setplength{sigbeforevskip}{\baselineskip} %--- skip between closing phrase and signature

@@

The manuscript introduces novel statistical methods and visualization techniques for assessing the ability of measurements, nowcasts, and forecasts to predict the correct direction of change.
These methods are exemplified using three distinct medical and healthcare datasets.
Hence, the manuscript aligns directly with the scope of BMC Medical Research Methodology.

>>>>

%--- set-up for the main part and the closing of the letter:
%\setkomavar{title}{Testtitel} %--- rarely needed, placed before the subject line
\setkomavar{subject}{Submission to BMC Medical Research Methodology} %--- placed before the opening phrase
\setkomavar{signature}{\includegraphics[width=2.5cm]{unterschrift}\\Jonas Rieger} %--- used by \closing{...}; overwrites the fromname variable
%\setkomavar{signature}{[signature to be inserted]\\Jonas Rieger} %--- used by \closing{...}; overwrites the fromname variable
                                             %(you can provide a hand-written signature with \includegraphics)
\setplength{sigbeforevskip}{\baselineskip} %--- skip between closing phrase and signature

@@

The manuscript introduces novel statistical methods and visualization techniques for assessing the ability of medical measurements, nowcasts, and forecasts to predict the correct direction of change.
These methods are exemplified using three distinct medical and healthcare datasets.
Hence, the manuscript aligns directly with the scope of BMC Medical Research Methodology.
